
---
title: "revisionAnalysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
.libPaths(c("/home/slacadie/.guix-profile/site-library"))
`%notin%` <- Negate(`%in%`)
library(tidyr)
library(dplyr)
library(RColorBrewer)
```


```{bash}
cp /fast/AG_Ohler/Lorena/CRISPR_phox2b/PAPER/*guide_results.txt ./
perl -lane 'next if $_ =~ /tart/;print "$F[0]\t$F[1]\t$F[2]\t$F[7]\t$F[11]\t$F[8]";' KRAB_guide_results.txt > KRAB_guide_results.bed
perl -lane 'next if $_ =~ /tart/;print "$F[10]\t$F[11]\t$F[12]\t$F[9]\t$F[4]";' aafInt800regionsMinFdr.txt > aafInt800regionsMinFdr.bed
bedtools closest -d -t "first" -a <(bedtools sort -i KRAB_guide_results.bed) -b <(bedtools sort -i ../mergedNbAllPeaks.bed) > KRAB_guide_results_closest.mergedNbAllPeaks.txt
bedtools closest -d -t "first" -a <(bedtools sort -i KRAB_guide_results.bed) -b <(bedtools sort -i ../mergedNbAtac_hg38.bed) > KRAB_guide_results_closest.mergedNbAtac.txt
```

```{r}
vpr = read.csv("/fast/AG_Ohler/Lorena/CRISPR_phox2b/PAPER/VPR_guide_results.txt", header=T, sep="\t")
krab = read.csv("/fast/AG_Ohler/Lorena/CRISPR_phox2b/PAPER/KRAB_guide_results.txt", header=T, sep="\t")
library(ggplot2)
pdf("vprKrabHexbinFdr.pdf")
fdrData = data.frame("vpr" = vpr$fdr,"krab"=krab$fdr)
ggplot(fdrData, aes(x=-log10(vpr), y=-log10(krab))) + geom_hex() + theme_minimal()
dev.off()
logfoldData = data.frame("vpr"=vpr$logfold, "krab"=krab$logfold)
pdf("vprKrabHexbinLfc.pdf")
ggplot(logfoldData, aes(x=vpr, y=krab)) + geom_hex() + theme_minimal()
dev.off()

krabRegionsGithub = read.csv("lorenaFromGithub/KRAB_regions_results_plot.csv", header=T, sep=",")
vprRegionsGithub = read.csv("lorenaFromGithub/VPR_regions_results_plot.csv", header=T, sep=",")
fdrRegionData = data.frame("vpr" = vprRegionsGithub$fdr,"krab"=krabRegionsGithub$fdr)
estimateData = data.frame("vpr" = vprRegionsGithub$estimate,"krab"=krabRegionsGithub$estimate)

pdf("vprKrabRegionHexbinFdr.pdf")
ggplot(fdrRegionData, aes(x=-log10(vpr), y=-log10(krab))) + geom_hex() + theme_minimal()
dev.off()

pdf("vprKrabRegionHexbinEstimate.pdf")
ggplot(estimateData, aes(x=vpr, y=krab)) + geom_hex() + theme_minimal()
dev.off()

load("../data.RData")
write.table(aafInt800regionsMinFdr, file="aafInt800regionsMinFdr.txt", quote=F, sep="\t", col.names=T, row.names=F)
bulkKrabNbIntersect = read.csv("./KRAB_guide_results_closest.mergedNbAllPeaks.txt", header=F, sep="\t")
bulkKrabNbIntersect$nb = "no"
bulkKrabNbIntersect[bulkKrabNbIntersect$V10 == 0,]$nb = "yes"
pdf("bulkKrabNbYesNoLfc.pdf")
ggplot(bulkKrabNbIntersect, aes(x=factor(nb), y=V6)) + geom_boxplot(outlier.shape=NA) + theme_minimal()
dev.off()
pdf("bulkKrabNbYesNoFdr.pdf")
ggplot(bulkKrabNbIntersect, aes(x=factor(nb), y=-log10(V5))) + geom_boxplot(outlier.shape=NA) + theme_minimal() + coord_cartesian(ylim=c(0,0.25))
dev.off()
bulkKrabNbAtacIntersect = read.csv("./KRAB_guide_results_closest.mergedNbAtac.txt", header=F, sep="\t")
bulkKrabNbAtacIntersect$atac = "no"
bulkKrabNbAtacIntersect[bulkKrabNbAtacIntersect$V10 == 0,]$atac = "yes"
pdf("bulkKrabNbAtacYesNoFdr.pdf")
library(ggplot2)
ggplot(bulkKrabNbAtacIntersect, aes(x=factor(atac), y=-log10(V5))) + geom_boxplot(outlier.shape=NA) + theme_minimal() + coord_cartesian(ylim=c(0,0.25))
dev.off()
pdf("bulkKrabNbAtacYesNoLfc.pdf")
ggplot(bulkKrabNbAtacIntersect, aes(x=factor(atac), y=V6)) + geom_boxplot(outlier.shape=NA) + theme_minimal()
dev.off()
aafInt800regions$prox = bulkRegionsGeneTss[match(aafInt800regions$ident, bulkRegionsGeneTss$V4),14]
aafInt800regions$closestGeneTss = bulkRegionsGeneTss[match(aafInt800regions$ident, bulkRegionsGeneTss$V4),10]
nrow(subset(aafInt800regions, aafInt800regions$prox == "intragenic" & aafInt800regions$closestGene == aafInt800regions$gene & aafInt800regions$sig == "sig"))
subset(aafInt800regions, aafInt800regions$prox == "intragenic" & aafInt800regions$closestGene == aafInt800regions$gene & aafInt800regions$sig == "sig")
nrow(subset(aafInt800regions, aafInt800regions$prox == "intragenic" & aafInt800regions$closestGene != aafInt800regions$gene & aafInt800regions$sig == "sig"))
```

```{bash}
bedtools intersect -wa -wb -a ../noNA_bulkRegions.bed -b ../gencode.v24.annotation.gtf.genes.bed | bedtools merge -i stdin -c 4,9 -o distinct,distinct > noNA_bulkRegions.genesIntersectMerged.bed



```

```{r}
bulkRegionsMergedGeneIntersect =  read.csv("./noNA_bulkRegions.genesIntersectMerged.bed",header=F, sep="\t")
aafInt800regions$geneIntersect = bulkRegionsMergedGeneIntersect[match(aafInt800regions$ident, bulkRegionsMergedGeneIntersect$V4),5]
aafInt800regions$geneIntersect = factor(aafInt800regions$geneIntersect)

levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="AC195454.1"] <- "LINC02265"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="UCHL1-AS1"] <- "UCHL1.AS1"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="LVCAT1"] <- "LINC02475"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-663P9.2"] <- "NDUFB4P12"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="ZBTB12P1"] <- "ZBTB12BP"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-700J17.2"] <- "AC096586.1"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-700J17.1"] <- "AC096586.2"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-814H16.2"] <- "AC106052.1"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-109E24.1"] <- "AC096734.1"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-333E13.2"] <- "AC098591.2"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-395I6.3"] <- "AC095057.3"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-324J13.1"] <- "AC098590.1"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-472B18.1"] <- "AC021148.1"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-539G18.3"] <- "AC108471.2"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-227F19.1"] <- "AC105389.3"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-109E24.2"] <- "AC096734.2"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-360F5.3"] <- "AC079921.2"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-63A11.1"] <- "AC024022.1"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-457P14.5"] <- "AC108210.1"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="APBB2,RP11-632F7.3"] <- "APBB2"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="PHOX2B,RP11-227F19.1,RP11-227F19.2"] <- "PHOX2B,AC105389.3"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-227F19.1,RP11-227F19.2"] <- "AC105389.3"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RNU1-49P,RP11-227F19.1"] <- "AC105389.3"
levels(aafInt800regions$geneIntersect)[levels(aafInt800regions$geneIntersect)=="RP11-457P14.6"] <- NA

aafInt800regions$geneIntersectIsTarget = mapply(function(x, y) grepl(x, y, fixed = T), aafInt800regions$gene, aafInt800regions$geneIntersect)

nrow(subset(aafInt800regions, aafInt800regions$sig == "sig" & aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$prox == "intragenic"))
#[1] 7
nrow(subset(aafInt800regions, aafInt800regions$sig == "sig" & aafInt800regions$geneIntersectIsTarget == "FALSE" & aafInt800regions$prox == "intragenic"))
#[1] 58

nrow(subset(aafInt800regions, aafInt800regions$sig == "sig" & aafInt800regions$geneIntersectIsTarget == "TRUE"))
#[1] 11
nrow(subset(aafInt800regions, aafInt800regions$sig == "sig" & aafInt800regions$geneIntersectIsTarget == "FALSE"))
#[1] 81

phox2bIntraRegions = unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$gene == "PHOX2B","ident"])

phox2bIntraRegionsCellsPurturbed <- unique(unlist(lapply(phox2bIntraRegions, function(col_name) {
  matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
  names(matCw@active.ident)[matching_rows]
})))

phox2bIntraRegionsCellsNotPurturbed = names(matCw@active.ident)[!names(matCw@active.ident) %in% phox2bIntraRegionsCellsPurturbed]

phox2bIntraList = list("targeted" = matCw@assays$SCT@data["PHOX2B",phox2bIntraRegionsCellsPurturbed], "not targeted" = matCw@assays$SCT@data["PHOX2B",phox2bIntraRegionsCellsNotPurturbed])
library(reshape2)
phox2bIntraListMelt = melt(phox2bIntraList)
pdf("phox2bIntra.pdf")
ggplot(phox2bIntraListMelt, aes(x = L1, y=value)) + geom_boxplot(outlier.shape = NA) + coord_cartesian(ylim = c(0,5)) + theme_classic() + xlab("PHOX2B intragenic CaREs") + ylab("log corrected PHOX2B counts per cell")
dev.off()

phox2bIntraProxRegions = unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$gene == "PHOX2B" & aafInt800regions$prox == "proximal","ident"])

phox2bIntraIntraRegions = unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$gene == "PHOX2B" & aafInt800regions$prox == "intragenic","ident"])

phox2bIntraProxRegionsCellsPurturbed <- unique(unlist(lapply(phox2bIntraProxRegions, function(col_name) {
  matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
  names(matCw@active.ident)[matching_rows]
})))

phox2bIntraIntraRegionsCellsPurturbed <- unique(unlist(lapply(phox2bIntraIntraRegions, function(col_name) {
  matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
  names(matCw@active.ident)[matching_rows]
})))

phox2bIntraProxList = list("proxTargeted" = matCw@assays$SCT@data["PHOX2B",phox2bIntraProxRegionsCellsPurturbed], "distTargeted" = matCw@assays$SCT@data["PHOX2B",phox2bIntraIntraRegionsCellsPurturbed], "notTargeted" = matCw@assays$SCT@data["PHOX2B",phox2bIntraRegionsCellsNotPurturbed])

phox2bIntraProxListMelt = melt(phox2bIntraProxList)

pdf("phox2bIntraProx.pdf")
ggplot(phox2bIntraProxListMelt, aes(x = L1, y=value)) + geom_boxplot(outlier.shape = NA) + coord_cartesian(ylim = c(0,5)) + theme_classic() + xlab("PHOX2B intragenic CaREs") + ylab("log corrected PHOX2B counts per cell")
dev.off()

#SHISA3

shisa3IntraRegions = unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$gene == "SHISA3","ident"])

shisa3IntraRegionsCellsPurturbed <- unique(unlist(lapply(shisa3IntraRegions, function(col_name) {
  matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
  names(matCw@active.ident)[matching_rows]
})))

shisa3IntraRegionsCellsNotPurturbed = names(matCw@active.ident)[!names(matCw@active.ident) %in% shisa3IntraRegionsCellsPurturbed]

shisa3IntraList = list("targeted" = matCw@assays$SCT@data["SHISA3",shisa3IntraRegionsCellsPurturbed], "not targeted" = matCw@assays$SCT@data["SHISA3",shisa3IntraRegionsCellsNotPurturbed])
shisa3IntraListMelt = melt(shisa3IntraList)

pdf("shisa3Intra.pdf")
ggplot(shisa3IntraListMelt, aes(x = L1, y=value)) + geom_boxplot(outlier.shape = NA) + coord_cartesian(ylim = c(0,5)) + theme_classic() + xlab("SHISA3 intragenic CaREs") + ylab("log corrected SHISA3 counts per cell")
dev.off()

shisa3IntraProxRegions = unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$gene == "SHISA3" & aafInt800regions$prox == "proximal","ident"])

shisa3IntraIntraRegions = unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$gene == "SHISA3" & aafInt800regions$prox == "intragenic","ident"])

shisa3IntraProxRegionsCellsPurturbed <- unique(unlist(lapply(shisa3IntraProxRegions, function(col_name) {
  matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
  names(matCw@active.ident)[matching_rows]
})))

shisa3IntraIntraRegionsCellsPurturbed <- unique(unlist(lapply(shisa3IntraIntraRegions, function(col_name) {
  matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
  names(matCw@active.ident)[matching_rows]
})))

shisa3IntraProxList = list("proxTargeted" = matCw@assays$SCT@data["SHISA3",shisa3IntraProxRegionsCellsPurturbed], "distTargeted" = matCw@assays$SCT@data["SHISA3",shisa3IntraIntraRegionsCellsPurturbed], "notTargeted" = matCw@assays$SCT@data["SHISA3",shisa3IntraRegionsCellsNotPurturbed])

shisa3IntraProxListMelt = melt(shisa3IntraProxList)

pdf("shisa3IntraProx.pdf")
ggplot(shisa3IntraProxListMelt, aes(x = L1, y=value)) + geom_boxplot(outlier.shape = NA) + coord_cartesian(ylim = c(0,5)) + theme_classic() + xlab("SHISA3 intragenic CaREs") + ylab("log corrected SHISA3 counts per cell")
dev.off()

#shisa3 phox2b double plot test

shisa3IntraProxListMelt$gene = "SHISA3"

phox2bIntraProxListMelt$gene = "PHOX2B"

phox2bShisa3IntraProxListMelt = rbind(shisa3IntraProxListMelt,phox2bIntraProxListMelt)

pdf("phox2bShisa3IntraProx.pdf")
ggplot(phox2bShisa3IntraProxListMelt, aes(x = gene, y=value, fill=L1)) + geom_boxplot(outlier.shape = NA) + coord_cartesian(ylim = c(0,5)) + theme_classic() + xlab("intragenic CaREs") + ylab("log corrected counts per cell")
dev.off()

#for all intragenic CaREs per gene
intraGenes = unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE","gene"])
intraGeneDf = data.frame()
for (gene in intraGenes){
    paste0(gene,"IntraRegions") = unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$gene == gene,"ident"])
    paste0(gene,"IntraRegionsCellsPurturbed") <- unique(unlist(lapply(paste0(gene,"IntraRegions"), function(col_name) {
  matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
  names(matCw@active.ident)[matching_rows]
})))
    paste0(gene,"IntraRegionsCellsNotPurturbed") = names(matCw@active.ident)[!names(matCw@active.ident) %in% paste0(gene,"IntraRegionsCellsPurturbed")]
    paste0(gene,"IntraProxRegions") = unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$gene == gene & aafInt800regions$prox == "proximal","ident"])
    paste0(gene,"IntraIntraRegions") = unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$gene == gene & aafInt800regions$prox == "intragenic","ident"])
    paste0(gene,"IntraProxRegionsCellsPurturbed") <- unique(unlist(lapply(paste0(gene,"IntraProxRegions"), function(col_name) {
  matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
  names(matCw@active.ident)[matching_rows]
})))
    paste0(gene,"IntraIntraRegionsCellsPurturbed") <- unique(unlist(lapply(paste0(gene,"IntraIntraRegions"), function(col_name) {
  matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
  names(matCw@active.ident)[matching_rows]
})))
    paste0(gene,"IntraProxList") = list("proxTargeted" = matCw@assays$SCT@data[gene,paste0(gene,"IntraProxRegionsCellsPurturbed")], "distTargeted" = matCw@assays$SCT@data[gene,paste0(gene,"IntraIntraRegionsCellsPurturbed")], "notTargeted" = matCw@assays$SCT@data[gene,paste0(gene,"IntraRegionsCellsNotPurturbed")])
    paste0(gene,"IntraProxListMelt") = melt(paste0(gene,"IntraProxList"))
    paste0(gene,"IntraProxListMelt")$gene = gene
    intraGeneDf = rbind(intraGeneDf,paste0(gene,"IntraProxListMelt"))
}


###chatGPT corrected code

# Ensure intraGeneDf is initialized
intraGeneDf <- data.frame()

# Loop through genes
for (gene in intraGenes) {
  
  # Dynamically create variables
  assign(paste0(gene, "IntraRegions"), 
         unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$gene == gene, "ident"]))
  
  assign(paste0(gene, "AllSigRegions"), 
         unique(aafInt800regions[aafInt800regions$sig == "sig" & aafInt800regions$gene == gene, "ident"]))
  
  assign(paste0(gene, "IntraRegionsCellsPurturbed"), 
         unique(unlist(lapply(get(paste0(gene, "IntraRegions")), function(col_name) {
           if (col_name %in% colnames(matCw@meta.data)) {
             matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
             names(matCw@active.ident)[matching_rows]
           } else {
             NULL
           }
         }))))
  
  assign(paste0(gene, "AllSigRegionsCellsPurturbed"), 
         unique(unlist(lapply(get(paste0(gene, "AllSigRegions")), function(col_name) {
           if (col_name %in% colnames(matCw@meta.data)) {
             matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
             names(matCw@active.ident)[matching_rows]
           } else {
             NULL
           }
         }))))

  assign(paste0(gene, "CombinedCellsPurturbed"),
         c(get(paste0(gene, "IntraRegionsCellsPurturbed")), get(paste0(gene, "AllSigRegionsCellsPurturbed"))))

  assign(paste0(gene, "IntraRegionsCellsNotPurturbed"), 
         names(matCw@active.ident)[!names(matCw@active.ident) %in% get(paste0(gene, "CombinedCellsPurturbed"))])
  
  assign(paste0(gene, "IntraProxRegions"), 
         unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$gene == gene & aafInt800regions$prox == "proximal", "ident"]))
  
  assign(paste0(gene, "IntraIntraRegions"), 
         unique(aafInt800regions[aafInt800regions$geneIntersectIsTarget == "TRUE" & aafInt800regions$gene == gene & aafInt800regions$prox == "intragenic", "ident"]))
  
  assign(paste0(gene, "IntraProxRegionsCellsPurturbed"), 
         unique(unlist(lapply(get(paste0(gene, "IntraProxRegions")), function(col_name) {
           if (col_name %in% colnames(matCw@meta.data)) {
             matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
             names(matCw@active.ident)[matching_rows]
           } else {
             NULL
           }
         }))))
  
  assign(paste0(gene, "IntraIntraRegionsCellsPurturbed"), 
         unique(unlist(lapply(get(paste0(gene, "IntraIntraRegions")), function(col_name) {
           if (col_name %in% colnames(matCw@meta.data)) {
             matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
             names(matCw@active.ident)[matching_rows]
           } else {
             NULL
           }
         }))))
  
  # Create a list and melt it
  intraProxList <- list(
    proxTargeted = matCw@assays$SCT@data[gene, get(paste0(gene, "IntraProxRegionsCellsPurturbed"))],
    distTargeted = matCw@assays$SCT@data[gene, get(paste0(gene, "IntraIntraRegionsCellsPurturbed"))],
    notTargeted = matCw@assays$SCT@data[gene, get(paste0(gene, "IntraRegionsCellsNotPurturbed"))]
  )
  
  melted_list <- melt(intraProxList)
  melted_list$gene <- gene
  
  # Append to intraGeneDf
  intraGeneDf <- rbind(intraGeneDf, melted_list)
}


pdf("allGenesIntraProx.pdf")
ggplot(intraGeneDf, aes(x = gene, y=value, fill=L1, color=L1)) + geom_boxplot() + coord_cartesian(ylim = c(0,6)) + theme_classic() + xlab("intragenic CaREs") + ylab("log corrected counts per cell")
dev.off()


#bend4IntraList = list("targeted" = matCw@assays$SCT@data["BEND4",bend4IntraRegionsCellsPurturbed], "not targeted" = matCw@assays$SCT@data["BEND4",bend4IntraRegionsCellsNotPurturbed])
#bend4IntraListMelt = melt(bend4IntraList)
#pdf("bend4Intra.pdf")
#ggplot(bend4IntraListMelt, aes(x = L1, y=value)) + geom_boxplot(outlier.shape = NA) + coord_cartesian(ylim = c(0,5)) + theme_classic() + xlab("BEND4 intragenic CaREs") + ylab("log corrected BEND4 counts per cell")
#dev.off()

#pdf("bend4IntraProx.pdf")
#ggplot(bend4IntraProxListMelt, aes(x = L1, y=value)) + geom_boxplot(outlier.shape = NA) + coord_cartesian(ylim = c(0,5)) + theme_classic() + xlab("BEND4 intragenic CaREs") + ylab("log corrected BEND4 counts per cell")
#dev.off()

geneMaxRhapCounts = apply(matCw@assays$SCT@data,1,max)

geneMeanRhapCounts = apply(matCw@assays$SCT@data,1,mean)

#promoter guides upstream vs downsteam??

#neighboring cares and their targets for spreading

#phox2b binding site cares in cells containing phox2b-actiavteing guides

```


##address spreading by looking target expression for closest CaREs that have different targets in cells where the primary care is targeted and not the secondary care
```{r}
write.table((unique(aafInt800regions[,c(11,12,13,7)])), file="rhapRegions.bed", quote=F, sep="\t", row.names=F, col.names=F)
```
```{bash}
bedtools closest -d -N -a <(bedtools sort -i rhapRegions.bed) -b <(bedtools sort -i rhapRegions.bed) > rhapRegions.bed_selfClosest.bed


```
```{r}
rhapRegionsSelfClosest = read.csv("rhapRegions.bed_selfClosest.bed", header=F, sep="\t")
aafInt800regions$careClosestCare = rhapRegionsSelfClosest[match(aafInt800regions$ident, rhapRegionsSelfClosest$V4),8]
aafInt800regions$careClosestCareDist = rhapRegionsSelfClosest[match(aafInt800regions$ident, rhapRegionsSelfClosest$V4),9]
sigRegionTargets = aafInt800regions[aafInt800regions$sig == "sig",] %>% group_by(ident) %>% summarise(targets = paste(unique(gene), collapse = ","))
sigRegionTargets = as.data.frame(sigRegionTargets)
aafInt800regions$careClosestCareTargets = sigRegionTargets[match(aafInt800regions$careClosestCare, sigRegionTargets$ident),2]
##this "same target" is decieving because primary CaRE is one line per target
aafInt800regions$careClosestCareTargetsSame = mapply(function(x, y) grepl(x, y, fixed = T), aafInt800regions$gene, aafInt800regions$careClosestCareTargets)

unique(aafInt800regions[aafInt800regions$sig == "sig" & !is.na(aafInt800regions$careClosestCareTargets), c(7,67,68,69,72)])
           ident careClosestCare careClosestCareDist  careClosestCareTargets          allCareTargets
61007   Region_1        Region_3                3671              PDS5A,TLR1      RBM47,NSUN7,RPS7P7
61715 Region_171      Region_174                9631                   APBB2               NDUFB4P12
61774 Region_174      Region_179                9129                    TLR1                   APBB2
63249   Region_3        Region_1                3671      RBM47,NSUN7,RPS7P7              PDS5A,TLR1
67851 Region_553      Region_557                4752                  PHOX2B        PHOX2B,LINC00682
68028 Region_561      Region_562                1557                  PHOX2B                  PHOX2B
69385 Region_668      Region_669                1133                   BEND4                  CHRNA9
69444 Region_669      Region_668                1133                  CHRNA9                   BEND4
69503 Region_671      Region_669                2254                   BEND4        BEND4,AC098590.1
70624 Region_729      Region_730                1020            BEND4,SHISA3         SHISA3,ZBTB12BP
71155 Region_740      Region_741                 826                  SHISA3            SHISA3,BEND4
71214 Region_741      Region_740                 826            SHISA3,BEND4                  SHISA3
71981 Region_789      Region_790                 654        SHISA3,TLR6,UGDH                  SHISA3
72040 Region_790      Region_789                 654                  SHISA3        SHISA3,TLR6,UGDH
72099 Region_803      Region_806                5134 SHISA3,TMEM156,PABPC1P1                  SHISA3
72158 Region_806      Region_803                5134                  SHISA3 SHISA3,TMEM156,PABPC1P1
72512 Region_828      Region_829                1266                  SHISA3   SHISA3,TLR6,LINC02265
72571 Region_829      Region_828                1266   SHISA3,TLR6,LINC02265                  SHISA3
72748 Region_836      Region_831                7172                  SHISA3                  ATP8A1

19 cases, 12 share a common gene, 11 less than 2.5 kb, 10 less than 2 kb, 4 less than 1 kb

```

###cares with phox2b binding from chip that do not target phox2b gene look in cells with phox2b targeting guides to see if the targets of these other cares are also activated, i.e. indirect effects
```{bash}
cat ../tfChips/filtered*PHOX* | cut -f1-3 | bedtools sort -i stdin | bedtools merge -i stdin > mergedFilteredPhox2bChips.bed
bedtools intersect -u -a rhapRegions.bed -b mergedFilteredPhox2bChips.bed > rhapRegionsWithPhox2bBinding.bed


```

```{r}
##from Uwe add examples of genes with significant cares that do not have phox2b binding sites###


phox2bBindingCares = read.csv("rhapRegionsWithPhox2bBinding.bed", header=F, sep="\t")
aafInt800regions$phox2bBinding = aafInt800regions$ident %in% phox2bBindingCares$V4

aafInt800regions$allCareTargets = sigRegionTargets[match(aafInt800regions$ident, sigRegionTargets$ident),2]
unique(aafInt800regions[aafInt800regions$sig == "sig" & aafInt800regions$phox2bBinding == "TRUE",c("ident","allCareTargets")])
#           ident                             allCareTargets
#65786 Region_477                                     PHOX2B
#66317 Region_494                             PHOX2B,SLC30A9
#66848 Region_512                                     PHOX2B
#67025 Region_520                                     PHOX2B
#67261 Region_530                           PHOX2B,LINC00682
#67497 Region_537                           PHOX2B,LINC00682
#67851 Region_553                           PHOX2B,LINC00682
#67910 Region_557                                     PHOX2B
#68028 Region_561                                     PHOX2B
#68205 Region_564 LINC00682,PHOX2B,RPS7P7,AC095057.3,SLC30A9
#71155 Region_740                               SHISA3,BEND4
#71214 Region_741                                     SHISA3
#72571 Region_829                                     SHISA3
#73692 Region_935                               WDR19,GNPDA2

#there are 4 cares that have ChIP binding sites for phox2b and do not significantly target Phox2b. so the question is in cells that have guides targeting phox2b, are these cares activated through secondary effects and thus their genes as well. 

aafInt800regions[aafInt800regions$sig == "sig" & aafInt800regions$gene == "PHOX2B",c("ident","avg_logFC","allCareTargets")]
#           ident  avg_logFC                             allCareTargets
#65786 Region_477  0.4677258                                     PHOX2B
#66317 Region_494 -0.5493911                             PHOX2B,SLC30A9
#66612 Region_504  0.3603152                                     PHOX2B
#66848 Region_512 -0.3404573                                     PHOX2B
#67025 Region_520  0.4048890                                     PHOX2B
#67261 Region_530 -0.3854239                           PHOX2B,LINC00682
#67497 Region_537 -0.3656320                           PHOX2B,LINC00682
#67851 Region_553  0.8111515                           PHOX2B,LINC00682
#67910 Region_557  0.6284872                                     PHOX2B
#68028 Region_561  0.5063157                                     PHOX2B
#68087 Region_562 -0.2376408                                     PHOX2B
#68206 Region_564  0.4317661 LINC00682,PHOX2B,RPS7P7,AC095057.3,SLC30A9
#74046  Region_99 -0.5605712                             PHOX2B,TMEM156



#genes targeted by CaREs that have phox2b binding sites and do not target phox2b:
phox2bSecTars = data.frame()
phox2bCares = aafInt800regions[aafInt800regions$sig == "sig" & aafInt800regions$gene == "PHOX2B","ident"]
phox2bCares = phox2bCares[ !phox2bCares == 'Region_99']
phox2bCareCells = unique(unlist(lapply(phox2bCares, function(col_name) {
           if (col_name %in% colnames(matCw@meta.data)) {
             matching_rows <- matCw@meta.data[[col_name]] == "perturbed"
             names(matCw@active.ident)[matching_rows]
           } else {
             NULL
           }
         })))
nonPhox2bCareCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% phox2bCareCells]

shisa3phoxList = list("phox2bCaREs" = matCw@assays$SCT@data["SHISA3", phox2bCareCells], "nonPhox2bCaREs" = matCw@assays$SCT@data["SHISA3", nonPhox2bCareCells])
shisa3phoxListMelted = melt(shisa3phoxList)
shisa3phoxListMelted$gene = "SHISA3"
phox2bSecTars = rbind(phox2bSecTars,shisa3phoxListMelted)

bend4phoxList = list("phox2bCaREs" = matCw@assays$SCT@data["BEND4", phox2bCareCells], "nonPhox2bCaREs" = matCw@assays$SCT@data["BEND4", nonPhox2bCareCells])
bend4phoxListMelted = melt(bend4phoxList)
bend4phoxListMelted$gene = "BEND4"
phox2bSecTars = rbind(phox2bSecTars,bend4phoxListMelted)

wdr19phoxList = list("phox2bCaREs" = matCw@assays$SCT@data["WDR19", phox2bCareCells], "nonPhox2bCaREs" = matCw@assays$SCT@data["WDR19", nonPhox2bCareCells])
wdr19phoxListMelted = melt(wdr19phoxList)
wdr19phoxListMelted$gene = "WDR19"
phox2bSecTars = rbind(phox2bSecTars,wdr19phoxListMelted)

gnpda2phoxList = list("phox2bCaREs" = matCw@assays$SCT@data["GNPDA2", phox2bCareCells], "nonPhox2bCaREs" = matCw@assays$SCT@data["GNPDA2", nonPhox2bCareCells])
gnpda2phoxListMelted = melt(gnpda2phoxList)
gnpda2phoxListMelted$gene = "GNPDA2"
phox2bSecTars = rbind(phox2bSecTars,gnpda2phoxListMelted)

pdf("phox2bSecTars.pdf")
ggplot(phox2bSecTars, aes(x = gene, y=value, fill=L1, color=L1)) + geom_boxplot() + coord_cartesian(ylim = c(0,6)) + theme_classic() + xlab("Phox2b target genes") + ylab("log corrected counts per cell")
dev.off()

#are any of the phox2b CaREs close to being significant for SHISA3
aafInt800regions[aafInt800regions$ident == "Region_477"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#           ident   gene   avg_logFC p_val_adj
#65829 Region_477 SHISA3 -0.01274492 0.9703414
aafInt800regions[aafInt800regions$ident == "Region_494"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#           ident   gene avg_logFC  p_val_adj
#66320 Region_494 SHISA3 0.0198781 0.08178146
aafInt800regions[aafInt800regions$ident == "Region_504"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#           ident   gene  avg_logFC p_val_adj
#66638 Region_504 SHISA3 0.02143778 0.6347887
aafInt800regions[aafInt800regions$ident == "Region_512"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#           ident   gene   avg_logFC p_val_adj
#66859 Region_512 SHISA3 -0.01816908 0.9308393
aafInt800regions[aafInt800regions$ident == "Region_520"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#           ident   gene   avg_logFC p_val_adj
#67058 Region_520 SHISA3 -0.01040432 0.7966449
aafInt800regions[aafInt800regions$ident == "Region_530"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#           ident   gene avg_logFC p_val_adj
#67263 Region_530 SHISA3  0.025461 0.1179445
aafInt800regions[aafInt800regions$ident == "Region_537"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#           ident   gene  avg_logFC p_val_adj
#67529 Region_537 SHISA3 0.01462557 0.7568072
aafInt800regions[aafInt800regions$ident == "Region_553"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#           ident   gene    avg_logFC p_val_adj
#67870 Region_553 SHISA3 -0.002552521 0.9236715
aafInt800regions[aafInt800regions$ident == "Region_557"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#           ident   gene    avg_logFC p_val_adj
#67944 Region_557 SHISA3 -0.001428921 0.9481563
aafInt800regions[aafInt800regions$ident == "Region_561"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#           ident   gene  avg_logFC p_val_adj
#68034 Region_561 SHISA3 0.03217789 0.2937052
aafInt800regions[aafInt800regions$ident == "Region_562"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#           ident   gene   avg_logFC p_val_adj
#68134 Region_562 SHISA3 0.004713765 0.8767456
aafInt800regions[aafInt800regions$ident == "Region_564"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#           ident   gene   avg_logFC p_val_adj
#68226 Region_564 SHISA3 -0.02907134 0.4020687
aafInt800regions[aafInt800regions$ident == "Region_99"  & aafInt800regions$gene == "SHISA3",c("ident","gene","avg_logFC","p_val_adj")]
#          ident   gene    avg_logFC p_val_adj
#74102 Region_99 SHISA3 -0.009147641  0.950516

##plot sec targets again only for phox2b promoter
phox2bPromSecTars = data.frame()
shisa3phoxPromList = list("phox2bPromCells" = matCw@assays$SCT@data["SHISA3", region494cells], "nonPhox2bPromCells" = matCw@assays$SCT@data["SHISA3", region494nonCells])
shisa3phoxPromListMelted = melt(shisa3phoxPromList)
shisa3phoxPromListMelted$gene = "SHISA3"
phox2bPromSecTars = rbind(phox2bPromSecTars,shisa3phoxPromListMelted)

bend4phoxPromList = list("phox2bPromCells" = matCw@assays$SCT@data["BEND4", region494cells], "nonPhox2bPromCells" = matCw@assays$SCT@data["BEND4", region494nonCells])
bend4phoxPromListMelted = melt(bend4phoxPromList)
bend4phoxPromListMelted$gene = "BEND4"
phox2bPromSecTars = rbind(phox2bPromSecTars,bend4phoxPromListMelted)

wdr19phoxPromList = list("phox2bPromCells" = matCw@assays$SCT@data["WDR19", region494cells], "nonPhox2bPromCells" = matCw@assays$SCT@data["WDR19", region494nonCells])
wdr19phoxPromListMelted = melt(wdr19phoxPromList)
wdr19phoxPromListMelted$gene = "WDR19"
phox2bPromSecTars = rbind(phox2bPromSecTars,wdr19phoxPromListMelted)

gnpda2phoxPromList = list("phox2bPromCells" = matCw@assays$SCT@data["GNPDA2", region494cells], "nonPhox2bPromCells" = matCw@assays$SCT@data["GNPDA2", region494nonCells])
gnpda2phoxPromListMelted = melt(gnpda2phoxPromList)
gnpda2phoxPromListMelted$gene = "GNPDA2"
phox2bPromSecTars = rbind(phox2bPromSecTars,gnpda2phoxPromListMelted)

pdf("phox2bPromSecTars.pdf")
ggplot(phox2bPromSecTars, aes(x = gene, y=value, fill=L1, color=L1)) + geom_boxplot() + coord_cartesian(ylim = c(0,6)) + theme_classic() + xlab("Phox2b target genes") + ylab("corrected counts per cell")
dev.off()

```

##probing strange observation about phox2b promoter care showing increased phox2b expression count distribution but lfc reported by MAST is negative
```{r}
aafInt800regions[aafInt800regions$sig == "sig" & aafInt800regions$gene == "PHOX2B",c("ident","dist","avg_logFC")]                                                                          
           ident     dist  avg_logFC
#65786 Region_477 4.535332  0.4677258
#66317 Region_494 2.413300 -0.5493911
#66612 Region_504 4.345550  0.3603152
#66848 Region_512 4.549579 -0.3404573
#67025 Region_520 4.671377  0.4048890
#67261 Region_530 4.811629 -0.3854239
#67497 Region_537 4.916670 -0.3656320
#67851 Region_553 5.031941  0.8111515
#67910 Region_557 5.055844  0.6284872
#68028 Region_561 5.092977  0.5063157
#68087 Region_562 5.107312 -0.2376408
#68206 Region_564 5.131346  0.4317661
#74046  Region_99 5.902330 -0.5605712
region477cells = matCw@meta.data[["Region_477"]] == "perturbed"
region477nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region477cells]
region477cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region477cells]                                                                                                                     
region477nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region477nonCells]                                                                                                               
summary(region477cellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.000   1.386   2.565   2.297   3.367   4.317 
summary(region477nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675

region494cells = matCw@meta.data[["Region_494"]] == "perturbed"
region494nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region494cells]
region494cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region494cells]  
region494nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region494nonCells] 
summary(region494cellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.000   1.386   2.565   2.256   3.296   4.754
summary(region494nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675


region504cells = matCw@meta.data[["Region_504"]] == "perturbed"
region504nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region504cells]
region504cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region504cells]
region504nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region504nonCells]
summary(region504cellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.000   1.099   2.485   2.222   3.367   4.543
summary(region504nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675

region512cells = matCw@meta.data[["Region_512"]] == "perturbed"
region512nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region512cells]
region512cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region512cells]
region512nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region512nonCells]
summary(region512cellsPhox2b)
summary(region512nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.000   1.099   2.398   2.178   3.296   4.489 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675

region520cells = matCw@meta.data[["Region_520"]] == "perturbed"
region520nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region520cells]
region520cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region520cells]
region520nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region520nonCells]
summary(region520cellsPhox2b)
summary(region520nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.000   1.099   2.303   2.068   3.091   4.394 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675

region530cells = matCw@meta.data[["Region_530"]] == "perturbed"
region530nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region530cells]
region530cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region530cells]
region530nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region530nonCells]
summary(region530cellsPhox2b)
summary(region530nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.000   1.099   2.398   2.139   3.198   4.796 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675

region537cells = matCw@meta.data[["Region_537"]] == "perturbed"
region537nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region537cells]
region537cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region537cells]
region537nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region537nonCells]
summary(region537cellsPhox2b)
summary(region537nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.9972  2.4849  2.1668  3.2958  4.7536 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675

region553cells = matCw@meta.data[["Region_553"]] == "perturbed"
region553nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region553cells]
region553cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region553cells]
region553nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region553nonCells]
summary(region553cellsPhox2b)
summary(region553nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.000   1.946   2.996   2.570   3.497   4.331 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675

region557cells = matCw@meta.data[["Region_557"]] == "perturbed"
region557nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region557cells]
region557cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region557cells]
region557nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region557nonCells]
summary(region557cellsPhox2b)
summary(region557nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.000   1.386   2.485   2.231   3.091   4.718 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675

region561cells = matCw@meta.data[["Region_561"]] == "perturbed"
region561nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region561cells]
region561cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region561cells]
region561nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region561nonCells]
summary(region561cellsPhox2b)
summary(region561nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.000   1.171   2.639   2.242   3.258   4.718 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675

region562cells = matCw@meta.data[["Region_562"]] == "perturbed"
region562nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region562cells]
region562cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region562cells]
region562nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region562nonCells]
summary(region562cellsPhox2b)
summary(region562nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.3026  1.9933  3.0910  4.3307 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675

region564cells = matCw@meta.data[["Region_564"]] == "perturbed"
region564nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region564cells]
region564cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region564cells]
region564nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region564nonCells]
summary(region564cellsPhox2b)
summary(region564nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.000   1.099   2.485   2.232   3.305   4.868 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675

region99cells = matCw@meta.data[["Region_99"]] == "perturbed"
region99nonCells = names(matCw@active.ident)[!names(matCw@active.ident) %in% region99cells]
region99cellsPhox2b = matCw@assays$SCT@data["PHOX2B", region99cells]
region99nonCellsPhox2b = matCw@assays$SCT@data["PHOX2B", region99nonCells]
summary(region99cellsPhox2b)
summary(region99nonCellsPhox2b)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.000   0.000   1.099   1.195   1.946   3.951 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0000  0.6931  2.0794  1.8562  2.9444  4.8675 

##check SCT$scale.data
region494cellsPhox2bScale = matCw@assays$SCT@scale.data["PHOX2B", region494cells]
region494nonCellsPhox2bScale = matCw@assays$SCT@scale.data["PHOX2B", region494nonCells]
summary(region494cellsPhox2bScale)
summary(region494nonCellsPhox2bScale)
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#-3.9368 -0.9969  0.1701  1.4294  3.2349 21.3349 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#-4.0104 -1.7344 -0.7747  0.0000  0.9944 21.3349


```

##check adjusted pvalue distribution for vpr bulk screen to look for multiple populations
```{r}
pdf("bulkRegionFdrDist.pdf")                                                                                                                                                               
ggplot(bulkRegions, aes(x=-log10(Region_fdr))) + geom_histogram(bins=100) + theme_classic()                                                                                                
dev.off()



```

##plot evidence for bulk results
```{r}
regionsMeulemanDhsEpiMapCreClosest$nbDist = bulkRegionsNbAll[match(regionsMeulemanDhsEpiMapCreClosest$id, bulkRegionsNbAll$V4),9]
regionsMeulemanDhsEpiMapCreClosest$nbClose = "no"
regionsMeulemanDhsEpiMapCreClosest[regionsMeulemanDhsEpiMapCreClosest$nbDist <= 250,]$nbClose = "yes"
regionsMeulemanDhsEpiMapCreClosest$evidence = "noEF"
regionsMeulemanDhsEpiMapCreClosest[regionsMeulemanDhsEpiMapCreClosest$nbClose == "yes",]$evidence = "nb"
regionsMeulemanDhsEpiMapCreClosest[regionsMeulemanDhsEpiMapCreClosest$class != "none" & regionsMeulemanDhsEpiMapCreClosest$nbClose == "no",]$evidence = "other"
regionsMeulemanDhsEpiMapCreClosest$evidence = factor(regionsMeulemanDhsEpiMapCreClosest$evidence, levels = c("nb", "other", "noEF"))

regionsMeulemanDhsEpiMapCreClosest$sig = "nonSig"
regionsMeulemanDhsEpiMapCreClosest[regionsMeulemanDhsEpiMapCreClosest$fdr < 0.05,23] = "sig"

pdf(file="bulkFdrByEvidenceBox.pdf")
ggplot(subset(regionsMeulemanDhsEpiMapCreClosest, regionsMeulemanDhsEpiMapCreClosest$sig == "sig"), aes(x=evidence, y=-log10(fdr))) + geom_boxplot(outlier.shape = NA) + theme_classic() + coord_cartesian(ylim = c(0,12))
dev.off()

pdf(file="bulkEvidenceByChrStateBar.pdf")
ggplot(subset(regionsMeulemanDhsEpiMapCreClosest, regionsMeulemanDhsEpiMapCreClosest$sig == "sig"), aes(x=evidence, fill=class)) + geom_bar() + theme_classic()
dev.off()

regionsMeulemanDhsEpiMapCreClosest$slope = bulkRegions[match(regionsMeulemanDhsEpiMapCreClosest$id,bulkRegions$Region_name),"Region_slope"]

pdf("bulkSlopeByEvidenceBox.pdf")
ggplot(subset(regionsMeulemanDhsEpiMapCreClosest, regionsMeulemanDhsEpiMapCreClosest$sig == "sig"), aes(x=evidence, y=slope)) + geom_boxplot(outlier.shape = NA) + theme_classic()
dev.off()



```

##plot martins signals from bulk sigNonSig
```{r}

martinsRegionSignals = read.csv("../../../martin_rhapsody/analysis/integrate_crispr_chips_atac/output/regions_ChIPs_ATAC_hg38.tsv.gz", header=T, sep="\t")
martinsRegionSignalsNoNa = martinsRegionSignals[!is.na(martinsRegionSignals$Region_fdr),]
martinsRegionSignalsNoNa$sig = "nonSig"
martinsRegionSignalsNoNa[martinsRegionSignalsNoNa$Region_fdr < 0.05,37] = "sig"

martinsRegionSignalsNoNa$sig = factor(martinsRegionSignalsNoNa$sig, levels = c("sig", "nonSig"))
pdf(file="bulkSigNonSigAtac.pdf")
ggplot(martinsRegionSignalsNoNa, aes(x=sig, y=SHSY5Y_ATAC_norm)) + geom_boxplot(outlier.shape = NA) + theme_classic() + coord_cartesian(ylim = c(0,250))
dev.off()

pdf(file="bulkSigNonSigK4me1.pdf")
ggplot(martinsRegionSignalsNoNa, aes(x=sig, y=SHSY5Y_H3K4me1_norm)) + geom_boxplot(outlier.shape = NA) + theme_classic() + coord_cartesian(ylim = c(0,40))
dev.off()

pdf(file="bulkSigNonSigK4me3.pdf")
ggplot(martinsRegionSignalsNoNa, aes(x=sig, y=SHSY5Y_H3K4me3_norm)) + geom_boxplot(outlier.shape = NA) + theme_classic() + coord_cartesian(ylim = c(0,10))
dev.off()

pdf(file="bulkSigNonSigK27ac.pdf")
ggplot(martinsRegionSignalsNoNa, aes(x=sig, y=SHSY5Y_H3K27ac_norm)) + geom_boxplot(outlier.shape = NA) + theme_classic() + coord_cartesian(ylim = c(0,20))
dev.off()

#hexbin plots as suggested by Dusa
pdf("bulkSigAtacFdrHexbin.pdf")
ggplot(subset(martinsRegionSignalsNoNa, martinsRegionSignalsNoNa$sig == "sig"), aes(x=-log10(Region_fdr),y=SHSY5Y_ATAC_norm)) + geom_hex() + theme_minimal()
dev.off()
pdf("bulkSigMe1FdrHexbin.pdf")
ggplot(subset(martinsRegionSignalsNoNa, martinsRegionSignalsNoNa$sig == "sig"), aes(x=-log10(Region_fdr),y=SHSY5Y_H3K4me1_norm)) + geom_hex() + theme_minimal()
dev.off()
pdf("bulkSigMe3FdrHexbin.pdf")
ggplot(subset(martinsRegionSignalsNoNa, martinsRegionSignalsNoNa$sig == "sig"), aes(x=-log10(Region_fdr),y=SHSY5Y_H3K4me3_norm)) + geom_hex() + theme_minimal()
dev.off()
pdf("bulkSig27acFdrHexbin.pdf")
ggplot(subset(martinsRegionSignalsNoNa, martinsRegionSignalsNoNa$sig == "sig"), aes(x=-log10(Region_fdr),y=SHSY5Y_H3K27ac_norm)) + geom_hex() + theme_minimal()
dev.off()

pdf("bulkSigAtacEstimateHexbin.pdf")
ggplot(subset(martinsRegionSignalsNoNa, martinsRegionSignalsNoNa$sig == "sig"), aes(x=Region_estimate,y=SHSY5Y_ATAC_norm)) + geom_hex() + theme_minimal()
dev.off()
pdf("bulkSigMe1EstimateHexbin.pdf")
ggplot(subset(martinsRegionSignalsNoNa, martinsRegionSignalsNoNa$sig == "sig"), aes(x=Region_estimate,y=SHSY5Y_H3K4me1_norm)) + geom_hex() + theme_minimal()
dev.off()
pdf("bulkSigMe3EstimateHexbin.pdf")
ggplot(subset(martinsRegionSignalsNoNa, martinsRegionSignalsNoNa$sig == "sig"), aes(x=Region_estimate,y=SHSY5Y_H3K4me3_norm)) + geom_hex() + theme_minimal()
dev.off()
pdf("bulkSig27acEstimateHexbin.pdf")
ggplot(subset(martinsRegionSignalsNoNa, martinsRegionSignalsNoNa$sig == "sig"), aes(x=Region_estimate,y=SHSY5Y_H3K27ac_norm)) + geom_hex() + theme_minimal()
dev.off()





```


###guide level bulk promoters krab and vpr
```{bash}
perl -lane 'next if $_ =~ /chromosome/;print "$F[0]\t$F[1]\t$F[2]\t$F[7]\t$F[8]\t$F[11]" if $F[11] < 0.05;' /fast/AG_Ohler/Lorena/CRISPR_phox2b/PAPER/KRAB_guide_results.txt > KRAB_guide_results_sig.bed
perl -lane 'next if $_ =~ /chromosome/;print "$F[0]\t$F[1]\t$F[2]\t$F[7]\t$F[8]\t$F[11]" if $F[11] < 0.05;' /fast/AG_Ohler/Lorena/CRISPR_phox2b/PAPER/VPR_guide_results.txt > VPR_guide_results_sig.bed

cut -f1-3,8 /fast/AG_Ohler/Lorena/CRISPR_phox2b/PAPER/KRAB_guide_results.txt | grep -v chromosome > bulkGuides.bed
bedtools intersect -u -a <(bedtools slop -b 1000 -i bulkGuides.bed -g /fast/AG_Ohler/Scott/hg38/hg38.chrom.sizes) -b ../gencode.v24.annotation.gtf.genes.bed_true5end.bed | cut -f4 > bulkGuidesPromProxIds.txt
bedtools intersect -u -a <(bedtools slop -b 500 -i ../noNA_bulkRegions.bed -g /fast/AG_Ohler/Scott/hg38/hg38.chrom.sizes) -b ../gencode.v24.annotation.gtf.genes.bed_true5end.bed | cut -f4 > bulkRegionsPromProxIds.txt



```
```{r}
guidesPromProx = read.csv("bulkGuidesPromProxIds.txt", header=F, sep="\t")
regionsPromProx= read.csv("bulkRegionsPromProxIds.txt", header=F, sep="\t")
vpr$prox = "dist"
vpr[vpr$NAME %in% guidesPromProx$V1,]$prox = "prox"
krab$prox = "dist"
krab[krab$NAME %in% guidesPromProx$V1,]$prox = "prox"
proxFdrData = data.frame("vpr" = vpr[vpr$prox == "prox", "fdr"], "krab" = krab[krab$prox == "prox","fdr"])

pdf("vprKrabPromProxHexbinFdr.pdf")
ggplot(proxFdrData, aes(x=-log10(vpr), y=-log10(krab))) + geom_hex() + theme_minimal()
dev.off()

proxLogfoldData = data.frame("vpr" = vpr[vpr$prox == "prox","logfold"], "krab" = krab[krab$prox == "prox","logfold"])
pdf("vprKrabPromProxHexbinLfc.pdf")
ggplot(proxLogfoldData, aes(x=vpr, y=krab)) + geom_hex() + theme_minimal()
dev.off()


krabRegionsGithub$prox = "dist"
krabRegionsGithub[krabRegionsGithub$Gene %in% regionsPromProx$V1,"prox"] = "prox"
vprRegionsGithub$prox = "dist"
vprRegionsGithub[vprRegionsGithub$Gene %in% regionsPromProx$V1,"prox"] = "prox"

proxFdrRegionData = data.frame("vpr" = vprRegionsGithub[vprRegionsGithub$prox == "prox","fdr"],"krab"=krabRegionsGithub[krabRegionsGithub$prox == "prox","fdr"])
proxEstimateData = data.frame("vpr" = vprRegionsGithub[vprRegionsGithub$prox == "prox","estimate"],"krab"=krabRegionsGithub[krabRegionsGithub$prox == "prox","estimate"])

pdf("vprKrabRegionPromProxHexbinFdr.pdf")
ggplot(proxFdrRegionData, aes(x=-log10(vpr), y=-log10(krab))) + geom_hex() + theme_minimal()
dev.off()

pdf("vprKrabRegionPromProxHexbinEstimate.pdf")
ggplot(proxEstimateData, aes(x=vpr, y=krab)) + geom_hex() + theme_minimal()
dev.off()



```

#is the phox2b promoter a hit in the krab screen
```{bash}

grep Region_494 ../../../Analysis/new/regions_bins_guides_results.txt | cut -f21 | sort -u > Region_494guides.txt
while read p;do echo "$p"; grep "$p" KRAB_guide_results.txt;done <Region_494guides.txt | less                                                                                          
while read p;do echo "$p"; grep "$p" VPR_guide_results.txt;done <Region_494guides.txt | less                                                                                          
while read p;do echo "$p"; grep "$p" VPR_guide_results_sig.bed;done <Region_494guides.txt | less



```

##weird plot for uwe about spreading
```{r}
write.table((unique(aafInt800regions[aafInt800regions$sig == "sig",c(11,12,13,7)])), file="rhapRegionsSig.bed", quote=F, sep="\t", row.names=F, col.names=F)
```
```{bash}
bedtools closest -d -N -a <(bedtools sort -i rhapRegionsSig.bed) -b <(bedtools sort -i rhapRegionsSig.bed) > rhapRegionsSig.bed_selfClosest.bed

```
```{r}
rhapRegionsSigSelfClosest = read.csv("rhapRegionsSig.bed_selfClosest.bed", header=F, sep="\t")
rhapRegionsSigSelfClosest$closestPairId = paste(rhapRegionsSigSelfClosest$V4, rhapRegionsSigSelfClosest$V8, sep = ";")
rhapRegionsSelfClosest$closestPairId = paste(rhapRegionsSelfClosest$V4, rhapRegionsSelfClosest$V8, sep = ";")

rhapRegionsSigSelfClosest$isClosest = rhapRegionsSigSelfClosest$closestPairId %in% rhapRegionsSelfClosest$closestPairId

sameTargetTest = aafInt800regions[aafInt800regions$sig == "sig",] %>% group_by(ident) %>% summarise(test = paste(unique(careClosestCareTargetsSame), collapse = ","))
sameTargetTest = as.data.frame(sameTargetTest)
sameTargetTest$sameTarget = "FALSE"
sameTargetTest[sameTargetTest$test != "FALSE",]$sameTarget = "TRUE"

rhapRegionsSigSelfClosest$sameTarget = sameTargetTest[match(rhapRegionsSigSelfClosest$V4, sameTargetTest$ident),3]

rhapRegionsSigSelfClosest$aTargets = sigRegionTargets[match(rhapRegionsSigSelfClosest$V4, sigRegionTargets$ident),2]
rhapRegionsSigSelfClosest$bTargets = sigRegionTargets[match(rhapRegionsSigSelfClosest$V8, sigRegionTargets$ident),2] 

pdf("weirdUwePlot.pdf")
ggplot(rhapRegionsSigSelfClosest, aes(x=isClosest, y=log10(V9),color=sameTarget)) + geom_jitter() + theme_minimal()
dev.off()

```

##back to krab
```{bash}
ibedtools intersect -wa -wb -a KRAB_guide_results_sig.bed -b <(perl -lane 'print "$F[0]\t$F[1]\t$F[2]\t$F[6]\t$F[7]" if $F[7] < 0.05;' ../regionGene.bedpe)
chr4    40908179        40908199        chr4.40908179.+ -7.05528243550119       1.39870887797014e-33    chr4    40908097        40909118        Region_78;RPS7P7        0.0251420847662003
chr4    41835720        41835740        chr4.41835716.+ -1.69743722997957       0.043925862663499       chr4    41831511        41835740        Region_537;PHOX2B       4.14560633027191e-14
chr4    41835720        41835740        chr4.41835716.+ -1.69743722997957       0.043925862663499       chr4    41831511        41835740        Region_537;LINC00682    0.00368855458481396
chr4    42302486        42302506        chr4.42302548.+ -3.28540221886225       3.27964390681318e-07    chr4    42302180        42303135        Region_738;SHISA3       0.00202223880292417
chr4    42425831        42425851        chr4.42425831.- -1.74048007834244       0.0372293376985595      chr4    42425513        42427164        Region_803;SHISA3       0.00159554362702583
chr4    42481335        42481355        chr4.42481298.+ -2.16146342269412       0.00379530940783988     chr4    42481173        42481736        Region_828;SHISA3       1.65921753635047e-06
chr4    42481335        42481355        chr4.42481298.+ -2.16146342269412       0.00379530940783988     chr4    42481173        42481736        Region_828;TLR6 0.00297221995518202
chr4    42481335        42481355        chr4.42481298.+ -2.16146342269412       0.00379530940783988     chr4    42481173        42481736        Region_828;LINC02265    0.00297221995518202
chr4    42496384        42496404        chr4.42496415.+ 2.49608121963491        0.0473383012637555      chr4    42496111        42496435        Region_831;SHISA3       5.57899763638636e-10
chr4    42503878        42503898        chr4.42503878.+ -2.01837852931485       0.00968553290281168     chr4    42503606        42504060        Region_836;ATP8A1       2.08927354522485e-06

perl -lane 'print $_ if $F[11] < 0.05;' KRAB_guide_results.txt | cut -f8 | grep -v NAME > sig_KRAB_guideIds.txt
while read p;do grep "$p" name_key_rhapsody.txt;done <sig_KRAB_guideIds.txt 
#chr4.40886174.- TGGAAAGGACGAAACACCGAAAACATAATTTCTGAACACGTTTTAGAGCTAGAAATAGCAAGTTAAAATAAGGC                                                      X35 # not in rhap
#chr4.41382572.+ TGGAAAGGACGAAACACCGTAGGTGTGGAAAGGAGGGGAGTTTTAGAGCTAGAAATAGCAAGTTAAAATAAGGC                                                      X508 # in rhap
#chr4.41433798.+ TGGAAAGGACGAAACACCGTCCAGATTTGAGGGAAGTCGGTTTTAGAGCTAGAAATAGCAAGTTAAAATAAGGC                                                      X510 # in rhap
#chr4.41990886.- TGGAAAGGACGAAACACCGAGGCTGAACTGGAAAGGCGGGTTTTAGAGCTAGAAATAGCAAGTTAAAATAAGGC                                                      X1019 #in rhap
#chr4.42425831.- TGGAAAGGACGAAACACCGTGCCTTGAGAAGGGGCAGTGGTTTTAGAGCTAGAAATAGCAAGTTAAAATAAGGC                                                      X920 # in rhap
#chr4.42473506.+ TGGAAAGGACGAAACACCGTTGTGAGCTTGGTCTCAGAGGTTTTAGAGCTAGAAATAGCAAGTTAAAATAAGGC                                                      X346 # in rhap
#chr4.42481298.+ TGGAAAGGACGAAACACCGGACAAGATAACCCAGGAAGGGTTTTAGAGCTAGAAATAGCAAGTTAAAATAAGGC                                                      X925 # in rhap
#chr4.42496415.+ TGGAAAGGACGAAACACCGAATGCAGAAGCAAAGCACGCGTTTTAGAGCTAGAAATAGCAAGTTAAAATAAGGC                                                      X354 # in rhap
#chr4.42503878.+ TGGAAAGGACGAAACACCGTAGACACCTAGGGAAGGTGCGTTTTAGAGCTAGAAATAGCAAGTTAAAATAAGGC                                                      X358 # in rhap

```

##bulk promoter hits
```{bash}
bedtools intersect -u -a <(bedtools slop -b 500 -i ../sig_noNA_bulkRegions.bed -g /fast/AG_Ohler/Scott/hg38/hg38.chrom.sizes) -b ../gencode.v24.annotation.gtf.genes.bed_true5end.bed > bulkRegionsSlop500PromoterHits.bed

./SubsetColXFromColY.pl bulkRegionsSlop500PromoterHits.bed ../../../Analysis/new/regions_results.txt 3 0 | cut -d ' ' -f1,3,4 | sort -u
#Region_1 2.778364648627946e-10 -0.025566425702765946
#Region_234 0.0014880800950941922 -0.023984568575235607
#Region_256 1.6444611498782617e-13 -0.023072612453615953
#Region_272 7.342784677877018e-4 -0.05118174726236607
#Region_273 0.0040117111984585615 -0.02033606062284719
#Region_35 0.0034342529391672037 -0.015572023024381567
#Region_494 4.096257927023982e-59 -0.041193128470207827
#Region_504 7.93692633270191e-9 -0.027212203238187675
#Region_518 0.0021815609728705826 -0.03216907288641364
#Region_566 3.054761843954166e-7 -0.020014680991815286
#Region_577 3.4343825164409367e-8 -0.03436530575593351
#Region_582 7.889928622735733e-8 -0.030176092373576865
#Region_603 8.851237480456368e-6 -0.038575252792186696
#Region_609 3.5573274472801413e-6 -0.024681271104997474
#Region_671 2.190652713213877e-20 -0.026210040794922413
#Region_786 9.471656644591901e-4 -0.02082253991162549
#Region_790 3.004129946039519e-7 -0.02409076319520438
#Region_903 7.825126850946496e-4 -0.02995195779513215
#Region_921 1.2962560918224394e-7 -0.028932682679010474

bedtools intersect -wa -wb -a <(bedtools slop -b 500 -i ../sig_noNA_bulkRegions.bed -g /fast/AG_Ohler/Scott/hg38/hg38.chrom.sizes) -b ../gencode.v24.annotation.gtf.genes.bed_true5end.bed
#chr4    40748815        40752721        Region_1        2.77836464862795e-10    chr4    40749896        40749897        NSUN7   .       +
#chr4    40826686        40828335        Region_35       0.0034342529391672      chr4    40826764        40826765        Y_RNA   .       -
#chr4    41215812        41217062        Region_234      0.00148808009509419     chr4    41216713        41216714        APBB2   .       -
#chr4    41255075        41258444        Region_256      1.64446114987826e-13    chr4    41256726        41256727        UCHL1-AS1       .       -
#chr4    41255075        41258444        Region_256      1.64446114987826e-13    chr4    41256412        41256413        UCHL1   .       +
#chr4    41302338        41303464        Region_272      0.000734278467787702    chr4    41303336        41303337        Y_RNA   .       -
#chr4    41302995        41304035        Region_273      0.00401171119845856     chr4    41303336        41303337        Y_RNA   .       -
#chr4    41748211        41753252        Region_494      4.09625792702398e-59    chr4    41748969        41748970        PHOX2B  .       -
#chr4    41748211        41753252        Region_494      4.09625792702398e-59    chr4    41748292        41748293        RP11-227F19.1   .       +
#chr4    41748211        41753252        Region_494      4.09625792702398e-59    chr4    41750344        41750345        RP11-227F19.2   .       +
#chr4    41770629        41772768        Region_504      7.93692633270191e-09    chr4    41772102        41772103        RNU1-49P        .       -
#chr4    41793880        41795037        Region_518      0.00218156097287058     chr4    41794772        41794773        AC105389.1      .       -
#chr4    41891926        41894915        Region_566      3.05476184395417e-07    chr4    41894578        41894579        RP11-457P14.5   .       -
#chr4    41922670        41925036        Region_577      3.43438251644094e-08    chr4    41924179        41924180        RP11-457P14.6   .       +
#chr4    41934779        41936464        Region_582      7.88992862273573e-08    chr4    41935119        41935120        TMEM33  .       +
#chr4    41981080        41982166        Region_603      8.85123748045637e-06    chr4    41981695        41981696        DCAF4L1 .       +
#chr4    41990287        41991860        Region_609      3.55732744728014e-06    chr4    41990471        41990472        SLC30A9 .       +
#chr4    42151289        42154921        Region_671      2.19065271321388e-20    chr4    42152877        42152878        BEND4   .       -
#chr4    42391182        42392340        Region_786      0.00094716566445919     chr4    42391267        42391268        RP11-63A11.1    .       -
#chr4    42396877        42399243        Region_790      3.00412994603952e-07    chr4    42397838        42397839        SHISA3  .       +
#chr4    42656677        42658144        Region_903      0.00078251268509465     chr4    42657104        42657105        ATP8A1  .       -
#chr4    42656677        42658144        Region_903      0.00078251268509465     chr4    42657495        42657496        RP11-109E24.2   .       +
#chr4    42705893        42707634        Region_921      1.29625609182244e-07    chr4    42706106        42706107        RP11-109E24.1   .       +
```
##do stat test on tesla histone mod box plots
```{r}
library(ggpubr)


pdf(file = "sigNonSigAtacBoxiWithStat.pdf")
ggplot(aafInt800regionsMinFdr, aes(x=sig, y=regionAtac)) + geom_boxplot(outlier.shape = NA) + stat_compare_means(label.y = 500,method = "wilcox.test", aes(label = paste0("p = ", after_stat(p.format))),comparisons=list(c(1,2))) + theme_classic() + coord_cartesian(ylim = c(0,600))
dev.off()

pdf(file = "sigNonSig27acBoxWithStat.pdf")
ggplot(aafInt800regionsMinFdr, aes(x=sig, y=regionH3K27ac)) + geom_boxplot(outlier.shape = NA) + stat_compare_means(label.y = 100,method = "wilcox.test", aes(label = paste0("p = ", after_stat(p.format))),comparisons=list(c(1,2))) + theme_classic() + coord_cartesian(ylim = c(0,300))
dev.off()

pdf(file = "sigNonSigMe1BoxWithStat.pdf")
ggplot(aafInt800regionsMinFdr, aes(x=sig, y=regionH3K4me1)) + geom_boxplot(outlier.shape = NA) + stat_compare_means(label.y = 150,method = "wilcox.test", aes(label = paste0("p = ", after_stat(p.format))),comparisons=list(c(1,2))) + theme_classic() + coord_cartesian(ylim = c(0,175))
dev.off()

pdf(file = "sigNonSigMe3BoxWithStat.pdf")
#ggplot(aafInt800regionsMinFdr, aes(x=sig, y=regionH3K4me3)) + geom_boxplot(outlier.shape = NA) + stat_compare_means(label.y = 10.5,method = "wilcox.test", aes(label = paste0("p = ", after_stat(p.format))),comparisons=list(c(1,2))) + theme_classic() + coord_cartesian(ylim = c(0,12))
ggplot(aafInt800regionsMinFdr, aes(x=sig, y=regionH3K4me3)) + geom_boxplot(outlier.shape = NA) + stat_compare_means(label.y.npc = "top",method = "wilcox.test", aes(label = paste0("p = ", after_stat(p.format))),comparisons=list(c(1,2))) + theme_classic()
dev.off()


```

##histogram of guides per care
```{r}
guideNumberPerCare = bulkRegionsBinsGuides %>% group_by(Region_name) %>% summarise(n = n())
pdf(file="guideNumberPerCareHist.pdf")
ggplot(guideNumberPerCare, aes(n)) + geom_histogram() + theme_classic()
dev.off()

bulkRegions$width = bulkRegions$Region_end - bulkRegions$Region_start

bulkRegions$guideNum = guideNumberPerCare[match(bulkRegions$Region_name, guideNumberPerCare$Region_name), 2]
bulkRegionsNoNA = subset(bulkRegions, bulkRegions$Region_pvalue != "NA")


pdf(file="guideNumberPerCareVsWidthHexbin.pdf")


```

##do stat tests on bulk evidence classes
```{r}

pdf(file="bulkFdrByEvidenceBoxWithStats.pdf")
ggplot(subset(regionsMeulemanDhsEpiMapCreClosest, regionsMeulemanDhsEpiMapCreClosest$sig == "sig"), aes(x=evidence, y=-log10(fdr))) + geom_boxplot() + stat_compare_means(label.y.npc = "top",method = "wilcox.test", aes(label = paste0("p = ", after_stat(p.format))),comparisons=list(c(1,2), c(1,3),c(2,3))) + theme_classic() 
dev.off()
#+ coord_cartesian(ylim = c(0,12))
#dev.off()

pdf("bulkSlopeByEvidenceBoxWithStats.pdf")
ggplot(subset(regionsMeulemanDhsEpiMapCreClosest, regionsMeulemanDhsEpiMapCreClosest$sig == "sig"), aes(x=evidence, y=slope)) + geom_boxplot() + stat_compare_means(label.y.npc = "top",method = "wilcox.test", aes(label = paste0("p = ", after_stat(p.format))),comparisons=list(c(1,2), c(1,3),c(2,3))) + theme_classic()
dev.off()

```



